Self-assembly of colloid-cholesteric composites: A route to switchable optical materials

### 2013-10-02 trunk/papers/2012-sandwich/support.tex
updated supporting material
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2160 40876441-3496-0410-a613-a2fca35b2ae2

In this work, the chirality and reduced temperature are always set to lie
within the blue phase I region of the equilibrium phase diagram. EXCEPT?

@@

Here, a narrow sandwich of fluid is placed between flat walls in
perpendicular to the narrow coordinate direction, and with periodic
boundaries in the other two directions. The system size used in all
cases is 256$^2 \times$56 lattice sites. Each simulation is a ``quench''
in a similar manner to that used in the bulk: the order parameter is
initialised randomly. The free energy parameters (see Table~\ref{table:params})
are again appropriate for (equilibrium) blue phase I
(chirality $\kappa = 0.8$ and
reduced temperature $\tau = -0.25$). The cholesteric pitch is set
to be $p = 64$, providing a slight better resolution than the bulk
simulations.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
         & $A_0$ & $\gamma$ & $K$ & $p$ & $\kappa$ & $\tau$ & $Wa/K$\\
\hline 
Bulk BPI & 0.01 & 3.086 & 0.007061 & 32$\sqrt{2}$ & 0.6902 & -0.2500 &
0.23, 2.3\\
\hline
Bulk Quench & 0.01 & 3.086 & 0.007061 & 32$\sqrt{2}$ & 0.6902 & -0.2500 &
0.23, 2.3 \\
\hline
Confined & 0.01 & 3.086 & 0.01897 & 64 & 0.8 & -0.2500 & 0.23, 2.3\\
\hline
External field & 0.004& 3.086 & 0.02 & 32 & -0.25 & 2.6 & 0.23\\ 
\hline
\end{tabular}
\end{center}
\caption{Free energy parameters used in the simulations. Bulk BPI
correspond to Fig.~1 (A-D), bulk quench to Fig.~1 (E--H); confined
geometries are shown in Fig.~2; and the external field case is
relevant for Fig.~3.}
\label{table:params}
\end{table}

@@

To obtain an energy scale, we choose $A_0 \simeq 10^6$~Pa, which is 
reasonable from Ref.~\cite{blue1} (this is also the choice in
Ref.~\cite{oliver2}). This choice leads to a simulation unit of
free energy (or stress) equal to $10^{8}$~Pa in Figs.~1 and~3.
From the energy and length scales one can map elastic constants to
physical units: for instance, the simulation in Fig.~1 corresponds to
a liquid crystal with splay, bend and twist (Frank) elastic constants
equal to 35 pN (or equivalently $K=$70~pN). That is,
\begin{equation}
\frac{a}{b^2} = \frac{27}{2 A_0\gamma} \sim 2-5 \times 10^{-6}
{\rm J}^{-1}\, {\rm m}^{3}.
\end{equation}
WHAT ARE a/b???

@@

To calibrate the electric field strength 
we equate the value of the dimensionless parameter ${\cal E}$ in our 
simulations with that of a hypothetical experiment.
Given the previous value for $A_0$, and a dielectric anisotropy of 10
(or equivalently $\epsilon_a=10\epsilon_0$, with $\epsilon_0$ the
dielectric permittivity of vacuum), we then obtain that an electric field
of 5~V/$\mu$m corresponds to a value of ${\cal E}\sim$0.01.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.8]{doubletwist.pdf}
\end{center}
\caption{
(A) Schematic representation of the director field
in a cholesteric (left) and within a double twist cylinder (right).
(B) Snapshot of the disclination network in an equilibrated 
blue phase I structure. (C) Same as (B) for an amorphous blue phase III
network.}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.35]{support-fig2.pdf}
\end{center}
\caption{As for main manuscript Fig.~1 A--D
(with liquid crystal order parameter
initialised to equilibrium blue phase I structure), but for the entire
simulation system of 128$^3$ lattice sites. (A)  solid volume fraction~1\%
and weak anchoring;  (B) 4\% solid volume fraction and weak anchoring;
(C) 1\% solid volume fraction and strong anchoring; (D) 4\% solid
volume fraction and strong anchoring. The view direction in the
main figure is from the left here. There is a reference
particle at the bottom left in each panel which does not take part
in the simulation.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.35]{support-fig3.pdf}
\end{center}
\caption{As for main manuscript Fig.~1 E--H (initialised via a ``quench''
to generate a disordered network), but for the entire simulation
system of 128$^3$ lattice sites. (E) solid volume fraction 1\% and
weak anchoring; (F) 4\% solid volume fraction and weak anchoring;
(G) 1\% solid volume fraction and strong anchoring; (H) 4\% solid
volume fraction and strong anchoring. Again, there is a reference
particle at the bottom left in each case which does not take part
in the simulation.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.42]{support-fig4.pdf}
\end{center}
\caption{As for main manuscript Fig.~2 A--D (confined geometry with normal
anchoring walls at both top and bottom), but for the entire simulation
system of 256$^2\times$56 lattice sites. Each shows a top view and
side view of the same simulation state. (A) solid volume fraction 1\%
and weak anchoring; (B) 4\% solid volume fraction and weak anchoring;
(C) 1\% solid volume fraction and strong anchoring; (D) 4\% solid
volume fraction and strong anchoring.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.42]{support-fig5.pdf}
\end{center}
\caption{As for main manuscript Fig.~2 E--H (confined geometry with planar
anchoring walls at both top and bottom), but for the entire simulation
system of 256$^2\times$56 lattice sites. Each shows a top view and
side view of the same simulation state. (E) colloid solid volume fraction 1\%
and weak anchoring; (F) 4\% solid volume fraction and weak anchoring;
(G) 1\% solid volume fraction and strong anchoring; (H) 4\% solid
volume fraction and strong anchoring.}
\end{figure}

\begin{figure}[t]
\begin{center}
%%\includegraphics[width=0.95\columnwidth]{s5.jpg}
\end{center}
\caption{Pair correlation function for weak ($WR/K=0.23$) and strong ($WR/K=2.3$) anchoring cases considered in the manuscript. (A,B) BPI initialisation with A) volume fraction $\phi=1${\%} and B) $\phi=5${\%}. (C,D) ``quenched system'' with C) $\phi=1${\%} and D) $\phi=5${\%}.}
\end{figure}

%{\bf Captions for Supplementary Movies}

>>>>

In this work, the chirality and reduced temperature are always set to lie
within the blue phase I region of the equilibrium phase diagram, except
for Fig. 3 in the main manuscript, where the switching of colloids in
blue phase III is studied.

@@

Here, a narrow sandwich of fluid is placed between flat walls in
perpendicular to the narrow coordinate direction, and with periodic
boundaries in the other two directions. The system size used in all
cases is 256$^2 \times$56 lattice sites. Each simulation is a ``quench''
in a similar manner to that used in the bulk: the order parameter is
initialised randomly. The free energy parameters (see Table~\ref{table:params})
are again appropriate for (equilibrium) blue phase I
(chirality $\kappa = 0.8$ and
reduced temperature $\tau = -0.25$). The cholesteric pitch is set
to be $p = 64$, providing a slightly better resolution than the bulk
simulations.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
         & $A_0$ & $\gamma$ & $K$ & $p$ & $\kappa$ & $\tau$ & $Wa/K$\\
\hline 
Bulk BPI & 0.01 & 3.086 & 0.007061 & 32$\sqrt{2}$ & 0.6902 & -0.2500 &
0.23, 2.3\\
\hline
Bulk Quench & 0.01 & 3.086 & 0.007061 & 32$\sqrt{2}$ & 0.6902 & -0.2500 &
0.23, 2.3 \\
\hline
Confined & 0.01 & 3.086 & 0.01897 & 64 & 0.8 & -0.2500 & 0.23, 2.3\\
\hline
External field & 0.004& 3.086 & 0.02 & 32 & 2.6 & -0.2500 & 0.23\\ 
\hline
\end{tabular}
\end{center}
\caption{Free energy parameters used in the simulations. Bulk BPI
correspond to Fig.~1 (A-D), bulk quench to Fig.~1 (E--H); confined
geometries are shown in Fig.~2; and the external field case is
relevant for Fig.~3.}
\label{table:params}
\end{table}

{\bf 4.4 Disclination rendering}

@@

To obtain an energy scale, we choose $A_0 \simeq 10^6$~Pa, which is 
reasonable from Ref.~\cite{blue1} (this is also the choice in
Ref.~\cite{oliver2}). This choice leads to a simulation unit of
free energy (or stress) equal to $10^{8}$~Pa in Figs.~1 and~3.
From the energy and length scales one can map elastic constants to
physical units: for instance, the simulation in Fig.~1 corresponds to
a liquid crystal with splay, bend and twist (Frank) elastic constants
equal to 35 pN (or equivalently $K=$70~pN). That is,
WHAT ARE a/b???

@@

To calibrate the electric field strength 
we equate the value of the dimensionless parameter ${\cal E}$ in our 
simulations with that of a hypothetical experiment.
Given the previous value for $A_0$, and a dielectric anisotropy of 20
(or equivalently $\epsilon_a=20\epsilon_0$, with $\epsilon_0$ the
dielectric permittivity of vacuum), we then obtain that an electric field
of 100 V/$\mu$m corresponds to a value of ${\cal E}\sim 0.4$ (considering
a value of $\gamma=3.0857$ as in Fig. 3 of the main text.

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[scale=0.8]{support-fig1.png}
\end{center}
\caption{
(A) Schematic representation of the director field
in a cholesteric (left) and within a double twist cylinder (right).
(B) Snapshot of the disclination network in an equilibrated 
blue phase I structure. (C) Same as (B) for an amorphous blue phase III
network.}
\end{figure}

\newpage

%\vfill\pagebreak

\begin{figure}[!h]
\begin{center}
\includegraphics[scale=0.35]{support-fig2.pdf}
\end{center}
\caption{As for main manuscript Fig.~1 A--D
(with liquid crystal order parameter
initialised to equilibrium blue phase I structure), but for the entire
simulation system of 128$^3$ lattice sites. (A)  solid volume fraction~1\%
and weak anchoring;  (B) 4\% solid volume fraction and weak anchoring;
(C) 1\% solid volume fraction and strong anchoring; (D) 4\% solid
volume fraction and strong anchoring. The view direction in the
main figure is from the left here. There is a reference
particle at the bottom left in each panel which does not take part
in the simulation.}
\end{figure}

\newpage

\begin{figure}[!h]
\begin{center}
\includegraphics[scale=0.35]{support-fig3.pdf}
\end{center}
\caption{As for main manuscript Fig.~1 E--H (initialised via a ``quench''
to generate a disordered network), but for the entire simulation
system of 128$^3$ lattice sites. (E) solid volume fraction 1\% and
weak anchoring; (F) 4\% solid volume fraction and weak anchoring;
(G) 1\% solid volume fraction and strong anchoring; (H) 4\% solid
volume fraction and strong anchoring. Again, there is a reference
particle at the bottom left in each case which does not take part
in the simulation.}
\end{figure}

\newpage

\begin{figure}[!h]
\begin{center}
\includegraphics[scale=0.49]{support-fig4.png}
\end{center}
\caption{Plot of the free energy (per BP unit cell) versus time
for the simulations corresponding to Fig. 1A-H in the main text
(the labels correspond to those in Fig. 1).
}
\end{figure}

\newpage

\begin{figure}[!h]
\begin{center}
\includegraphics[scale=0.42]{support-fig5.pdf}
\end{center}
\caption{As for main manuscript Fig.~2 A--D (confined geometry with normal
anchoring walls at both top and bottom), but for the entire simulation
system of 256$^2\times$56 lattice sites. Each shows a top view and
side view of the same simulation state. (A) solid volume fraction 1\%
and weak anchoring; (B) 4\% solid volume fraction and weak anchoring;
(C) 1\% solid volume fraction and strong anchoring; (D) 4\% solid
volume fraction and strong anchoring.}
\end{figure}

\newpage

\begin{figure}[!h]
\begin{center}
\includegraphics[scale=0.42]{support-fig6.pdf}
\end{center}
\caption{As for main manuscript Fig.~2 E--H (confined geometry with planar
anchoring walls at both top and bottom), but for the entire simulation
system of 256$^2\times$56 lattice sites. Each shows a top view and
side view of the same simulation state. (E) colloid solid volume fraction 1\%
and weak anchoring; (F) 4\% solid volume fraction and weak anchoring;
(G) 1\% solid volume fraction and strong anchoring; (H) 4\% solid
volume fraction and strong anchoring.}
\end{figure}

\newpage

\if{\begin{figure}[!h]
\begin{center}
%%\includegraphics[width=0.95\columnwidth]{s5.jpg}
\end{center}
\caption{Pair correlation function for weak ($WR/K=0.23$) and strong ($WR/K=2.3$) anchoring cases considered in the manuscript. (A,B) BPI initialisation with A) volume fraction $\phi=1${\%} and B) $\phi=5${\%}. (C,D) ``quenched system'' with C) $\phi=1${\%} and D) $\phi=5${\%}.}
\end{figure}
}\fi

%\newpage

{\bf Captions for Supplementary Movies} \\

{\bf Supplementary Movie 1:} 
Final state of the end of the simulation in Fig.~1A. The movie
shows a rotation of the configuration to better appreciate details.\\

{\bf Supplementary Movie 2:} 
Final state of the end of the simulation in Fig.~1B. The movie
shows a rotation of the configuration to better appreciate details.\\

{\bf Supplementary Movie 3:} 
Final state of the end of the simulation in Fig.~1C. The movie
shows a rotation of the configuration to better appreciate details. \\

{\bf Supplementary Movie 4:} 
Final state of the end of the simulation in Fig.~1D. The movie
shows a rotation of the configuration to better appreciate details. \\

{\bf Supplementary Movie 5:} 
Final state at the end of the initial relaxation phase in Fig.~3. The movie
shows a rotation of the configuration to better appreciate details. The distribution of the colloidal particles is isotropic with the particles forming clusters and having a tendency to occupy positions a the intersection of the BPIII disclination lines.\\

{\bf Supplementary Movie 6:} 
Configuration in a homogeneous electric field with strength
corresponding to ${\cal E}=0.8$. The movie
shows a rotation of the configuration to better appreciate details.
A hexagonal pattern emerges where the particles form chains
situated at the vertices of the honeycomb-like structure. \\
